---
title: "Shared Tweets: An Analysis of Global Twitter Data"
author: "Jasper Palmer, Toan Ly, Ruizhe Zhou, and Nhat Le"
date: "2/28/2020"
output: html_document
---

```{r intro, echo = F, message = F}
library("knitr")
senators_df <- read.csv("data/senators.csv", stringsAsFactors = F,
                        check.names = F)
russian_trolls <- read.csv("data/IRAhandle_tweets_1.csv", stringsAsFactors = F,
                           check.names = F)
sentimental_df <- read.csv("data/sentimental140.csv", stringsAsFactors = F,
                           check.names = F)
```

<style>
.html-widget {
    margin: auto;
    margin-top: 25px;
    margin-bottom: 25px;
}
</style>

# Introduction

The domain that we are focusing on is Twitter data as it is a highly popular 
social media platform that gives us an insight to individuals mindset through 
short text summaries called tweets. These individuals include influential public
figures such as senators, as well as, any person that chooses to use the 
platform. This gives us data on social media usage in a standardized format that
will allow us to draw conclusions about a wide variety of individuals. Twitter 
is also an optimal choice because it is a primarily text based allowing us to 
analyze information rather than missing a whole subsection of context 
such as Instagram’s focus on pictures.

# Summary Information

```{r senators_list, echo = FALSE, message = F}
source("scripts/summary-paragraph.R")
list_senators<-get_senators_info(senators_df)
```
For the senators dataset, the length of this data is `r list_senators[["length"]]`. The average number of replies for all of those tweets is `r list_senators[["average_reply"]]`. We also analyzed the maximum and minimum number of favorites those tweets received, and the highest number of favorites is `r list_senators[["largest_favorites"]]`, while the lowest number of favorites is just `r list_senators[["fewest_favorites"]]`. The largest number of retweets a tweet recieved is `r list_senators[["largest_retweets"]]`, and the fewest number of retweets is also `r list_senators[["fewest_retweets"]]`. At last, we analyzed which party posted most tweets in this period, and that is `r list_senators[["popular_party"]]`, which represents the democratic party. 

 

```{r russian_list, echo = FALSE, message = F}
source("scripts/summary-paragraph.R")
list_russian <- get_russian_info(russian_trolls)
```
For the russian trolls dataset we used, the length of this data is `r list_russian[["length"]]`. We focused on the users more this time. The average of number of followers those users have is `r list_russian[["average_num_followers"]]`, and they follow `r list_russian[["average_num_following"]]` people in average. The user who has the highest number of followers has `r list_russian[["max_followers"]]` followers, but the user who has the lowest number of followers doesn't have any followers, with a number of `r list_russian[["fewest_followers"]]`. The most committed user, the person who posted the most tweets, is `r list_russian[["good_writer"]]`.

 

```{r sentiment_list, echo = FALSE, message = F}
source("scripts/summary-paragraph.R")
list_sentimental <- get_sentimental_info(sentimental_df)
```
Last but not least, for the sentimental dataset, the length of this data is `r list_sentimental[["length"]]`, and the columns are: `r list_sentimental[["column_name"]]`. There are a total number of `r list_sentimental[["total_positive"]]` for tweets that indicate positive mood, and there are `r list_sentimental[["total_negative"]]` negative mood tweets. We also analyzed the most prefered and least prefered day in a week to post tweets in general, and the most popular day is `r list_sentimental[["most_prefered_day"]]`, while the least prefered day to post tweets is `r list_sentimental[["least_prefered_day"]]`. 

# Summary Table

```{r summary_table_hashtag, echo = F, message = F} 
source("scripts/summary-table.R")
hashtag_vs_retweet_table(senators_df)
```
  
From the table we can see that there is a negative relationship between
the number of hashtags in a tweet and its average number of retweets in
general (except for the number of 8, which can be seen as an outlier). 
We employ this table to give a sense of how different number of hashtags 
influence the corresponding average number of retweets in an intuitional way. 
  
```{r table_desc_hashtag, echo = F, message = F} 
source("scripts/summary-table.R")
region_numbertweets_table(russian_trolls)
```
  
From this table we can directly see each region's total number of tweets 
in a descending order. The U.S. has the largest number of qualified tweets 
in this period and Egypt has the lowest number. We choose to employ this 
table because it is able to provide information about different countries' 
number of tweets in an extremely clear way. 
  
```{r summary_table_mood, echo = F, message = F} 
source("scripts/summary-table.R")
kable(sentimental_table(sentimental_df), 
      col.names =c("Is the Mood Positive?","Number of Tweets"), align = "l")
```
  
Table obtained from this dataset is a bit hard to compute. However, this 
table can present a direct illustration about the total number of tweets 
that are in positive mood as well as the total number of tweets that are 
in negative mood. It is meaningful because this table provides some deep 
idea about tweets, or social media in general, which is people's tendency 
to post something negative rather than positive.

# Does a Tweet's Hashtags Affect its Retweets?

This bar chart was intended to show the relationship between the number
of hashtags (discrete) that a tweet receives and the number of retweets
(discrete) that it gets.

```{r first_chart, echo = F, message = F}
source("scripts/first-chart.R")
hashtag_vs_retweet(senators_df)
```

As we can see from the chart, the overall trend (excluding the outlier of eight
hashtags) is a significant decline in average number of retweets per tweet for
each hashtag used a U.S. Senator's post. This trend is not consistent with the
number of retweets for the eight hashtag tweets, however, there were only six
tweets with eight hashtags and one tweet happened to have thousands of retweets which
heavily skewed its average result. Another interesting observation is that when
there were no hashtags in a tweet it received a much higher number of average
retweets and that by adding even one hashtag to a senator’s tweet it greatly
decreases their average number of retweets. This is interesting because hashtags
are intended to increase visibility and promote awareness, however, in this
small sample we see the opposite trend of decreased exposure that could be
attributed to a variety of outside factors.

# How time affects mood

```{r, echo = F, message = F}
source("scripts/second-chart.R")
mood(sentimental_df)
stats_mood(sentimental_df, "0")
stats_mood(sentimental_df, "4")
```

*Note: After the box plot, the first box is the statistics for the negative mood
plot and the second box is the statistics for the positive mood.

The reason why a box plot is good at displaying how time affects the mood is
because it shows the median hour, all the quartiles, minimum, and maximum
values which should provide quick statistics for any reader who just wants the
quick result. Based on the box plot and the summary below, the median for
negative mood tweets is at hour `r get_median(sentimental_df, "0")`
(`r rebuild_datetime(get_median(sentimental_df, "0"))`) and the median for
positive mood tweets is at hour `r get_median(sentimental_df, "4")`
(`r rebuild_datetime(get_median(sentimental_df, "4"))`). The box plot for
negative mood is skewed to the later time in the day which could indicate that
due to a long work day or school day, people tend to be in a negative mood. The
opposite is expected for positive mood as people are just freshed out of bed.

# [Chart Name 3]

```{r third_chart, echo = F} 
#Add function call here
source("scripts/third-chart.R")
```




